Comparison of several stochastic and deterministic derivative-free global optimization algorithms\thanks{The study was supported by the Russian Science Foundation, project No 16-11-10150.}

### 2019-02-13 2019/MOTOR_Sovrasov/motor_paper.tex
MOTOR: add OC plots

>>>>

\begin{figure}[ht]
  \centering
  \subfloat[4d Simple]{{\includegraphics[width=.5\textwidth]{images/gklss4d.pdf}}\label{fig:s4d}}
  \subfloat[4d Hard]{{\includegraphics[width=.5\textwidth]{images/gklsh4d.pdf}}\label{fig:h4d}}
  \caption{Operating characteristics of the algorithms when solving problems from the GKLS 4d classes}
\end{figure}

\begin{figure}[ht]
  \centering
  \subfloat[5d Simple]{{\includegraphics[width=.5\textwidth]{images/gklss5d.pdf}}\label{fig:s4d}}
  \subfloat[5d Hard]{{\includegraphics[width=.5\textwidth]{images/gklsh5d.pdf}}\label{fig:h4d}}
  \caption{Operating characteristics of the algorithms when solving problems from the GKLS 5d classes}
\end{figure}
